Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-03-17 MCQMC2022ChallengesQMCSoftwareArticle.tex
Updates from Overleaf
sc: add an affiliation

%%%%%%% Author sign off on this first submission, last revision
% Sou-Cheng Choi signed off on
% Yuhan Ding signed off on
% Fred J. Hickernell signed off on 3/17
% Jagadeeswaran Rathinavel signed off on
% Aleksei Sorokin signed off on 3/17/2023

@@

\title*{Challenges in Developing Great Quasi-Monte Carlo Software}
\authorrunning{S.-C.\ T.\ Choi et al.}
\author{Sou-Cheng T.~Choi \and Yuhan Ding \and Fred J. Hickernell \and Jagadeeswaran  Rathinavel \and Aleksei G. Sorokin}
\institute{
Sou-Cheng T.~Choi \at Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{schoi32@iit.edu}
\and
Yuhan Ding \at
 Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{yding2@hawk.iit.edu}
\and
Fred J. Hickernell \at Center for Interdisciplinary Scientific Computation and \\
Department of Applied Mathematics, Illinois Institute of Technology \\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{hickernell@iit.edu}
\and
Jagadeeswaran  Rathinavel \at
Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{jrathin1@hawk.iit.edu}
\and
Aleksei G. Sorokin \at
Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{asorokin@hawk.iit.edu}}

@@

>>>>

%%%%%%% Author sign off on this first submission, last revision 3/17/2023
% Sou-Cheng Choi signed off on 3/17/20223
% Yuhan Ding signed off on
% Fred J. Hickernell signed off on 3/17/2023
% Jagadeeswaran Rathinavel signed off on
% Aleksei Sorokin signed off on 3/17/2023

@@

\title*{Challenges in Developing Great Quasi-Monte Carlo Software}
\authorrunning{S.-C.\ T.\ Choi et al.}
\author{Sou-Cheng T.~Choi \and Yuhan Ding \and Fred J. Hickernell \and Jagadeeswaran  Rathinavel \and Aleksei G. Sorokin}
\institute{
Sou-Cheng T.~Choi \at Department of Applied Mathematics, Illinois Institute of Technology; SAS Institute Inc. \\RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{schoi32@iit.edu}
\and
Yuhan Ding \at
 Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{yding2@hawk.iit.edu}
\and
Fred J. Hickernell \at Center for Interdisciplinary Scientific Computation and \\
Department of Applied Mathematics, Illinois Institute of Technology \\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{hickernell@iit.edu}
\and
Jagadeeswaran  Rathinavel \at
Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{jrathin1@hawk.iit.edu}
\and
Aleksei G. Sorokin \at
Department of Applied Mathematics, Illinois Institute of Technology,\\ RE 220, 10 W.\ 32$^{\text{nd}}$ St., Chicago, IL 60616 \email{asorokin@hawk.iit.edu}}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{latticepts.eps}
    \caption{A two-dimensional projection of}
    \label{fig:latticepts}
\end{figure}
